---
title: "Spectrometer Calibration Report"
author: "NIR Intelligence Platform"
format: html
date: "`r Sys.Date()`"
---

# Spectrometer Calibration Report

## Calibration Overview

Instrument: `r params$instrument_type`
Calibration Date: `r params$calibration_date`

## Calibration Results

### Performance Metrics
- **R² Score**: `r params$r2_score`
- **RMSE**: `r params$rmse`
- **Calibration Points**: `r params$calibration_points`

### Parameter Recommendations

#### Current Parameters
`r ifelse(length(params$current_parameters) > 0, paste("- ", names(params$current_parameters), ": ", unlist(params$current_parameters), collapse = "\n- "), "No current parameters")`

#### Recommended Parameters
`r ifelse(length(params$recommended_parameters) > 0, paste("- ", names(params$recommended_parameters), ": ", unlist(params$recommended_parameters), collapse = "\n- "), "No recommendations")`

## Calibration Curves

```{r}
if (exists("params$wavelengths") && exists("params$measured") && exists("params$reference")) {
  plot(params$wavelengths, params$measured, type = "l", col = "blue", 
       xlab = "Wavelength (nm)", ylab = "Intensity", 
       main = "Calibration Curve", ylim = range(min(c(params$measured, params$reference)), 
                                                max(c(params$measured, params$reference))))
  lines(params$wavelengths, params$reference, col = "red")
  legend("topright", legend = c("Measured", "Reference"), col = c("blue", "red"), lty = 1)
}
```

## Validation Results

### Cross-Validation
- **Mean R²**: `r params$cv_mean_r2`
- **Std Dev R²**: `r params$cv_std_r2`
- **Validation Samples**: `r params$validation_samples`

### Residual Analysis
```{r}
if (exists("params$residuals")) {
  hist(params$residuals, main = "Residual Distribution", xlab = "Residuals")
}
```
