---
title: "Comprehensive NIR Analysis Report"
author: "NIR Intelligence Platform"
format: html
date: "`r Sys.Date()`"
---

# Comprehensive NIR Analysis Report

## Executive Summary

Sample ID: `r params$sample_id`

This comprehensive report combines spectral analysis and metadata quality assessment to provide a complete evaluation of your NIR data.

## Spectral Analysis Results

### Quality Assessment

- **Quality Score**: `r params$spectral_quality_score` (`r params$spectral_quality_grade`)
- **Wavelength Range**: `r params$wavelength_range[1]` - `r params$wavelength_range[2]` nm
- **Data Points**: `r params$data_points`

### Detected Issues

`r ifelse(length(params$spectral_issues) > 0, paste("- ", params$spectral_issues, collapse = "
- "), "No spectral issues detected")`

## Metadata Quality Results

### Overall Quality

- **Score**: `r params$metadata_quality_score` (`r params$metadata_quality_grade`)
- **Completeness**: `r params$metadata_completeness_score`%
- **Accuracy**: `r params$metadata_accuracy_score`%
- **Consistency**: `r params$metadata_consistency_score`%

### Standards Compliance

`r for (standard in names(params$metadata_standards)) {
  cat("- **", standard, "**: ", round(params$metadata_standards[[standard]], 1), "%
")
}`

## Combined Recommendations

### Spectral Recommendations

`r ifelse(length(params$spectral_recommendations) > 0, paste("- ", params$spectral_recommendations, collapse = "
- "), "No spectral recommendations")`

### Metadata Recommendations

`r ifelse(length(params$metadata_recommendations) > 0, paste("- ", params$metadata_recommendations, collapse = "
- "), "No metadata recommendations")`

## Data Visualization

### Spectral Data

```{r}
if (exists("params$wavelengths") && exists("params$intensities")) {
  plot(params$wavelengths, params$intensities, type = "l",
        xlab = "Wavelength (nm)", ylab = "Intensity",
        main = "Spectral Data")
}
```

## Data

### Measured Data Points

```{r}
spectral_df <- data.frame(
  Wavelength_nm = params$wavelengths,
  Intensity = params$intensities
)
print(head(spectral_df, n = 50))
```

## Evaluation Results

### Sensor Quality Assessment

```{r}
sensor_quality <- params$sensor_quality_results
if (!is.null(sensor_quality)) {
  cat("Status: ", sensor_quality$status, "
")
  cat("Overall Quality Score: ", round(sensor_quality$overall_quality_score, 3), "
")
  cat("Drift detected: ", sensor_quality$drift_detected, "
")
  cat("Offset detected: ", sensor_quality$offset_detected, "
")
  cat("Noise level: ", round(sensor_quality$noise_level, 4), "
")
}
```

### Statistical Analysis

```{r}
statistical <- params$statistical_analysis_results
if (!is.null(statistical)) {
  cat("Methods applied: ", paste(statistical$methods_applied, collapse = ", "), "
")
  cat("Samples: ", statistical$num_samples, "
")
  cat("Data points: ", statistical$data_points, "
")
}
```

### Neural Network Evaluation

```{r}
neural <- params$neural_network_results
if (!is.null(neural)) {
  cat("Status: ", neural$status, "
")
  if (!is.null(neural$r2_score)) cat("R2 Score: ", round(neural$r2_score, 3), "
")
  if (!is.null(neural$reconstruction_mse)) cat("Reconstruction MSE: ", round(neural$reconstruction_mse, 4), "
")
  if (!is.null(neural$anomalies_detected)) cat("Anomalies detected: ", neural$anomalies_detected, "
")
}
```

## Source Code

### Analysis Source Code

The complete Python source code of the agents used for this analysis is included below for reproducibility.

```
`r params$analysis_source_code`
```

## Appendix

### Processing Parameters

```{r}
analysis_params <- list(
  analysis_mode = params$analysis_mode,
  report_type = params$report_type,
  privacy_level = params$privacy_level,
  include_calibration = params$include_calibration
)
str(analysis_params)
```

