---
title: "Comprehensive NIR Analysis Report"
author: "NIR Intelligence Platform"
format: html
date: "`r Sys.Date()`"
---

# Comprehensive NIR Analysis Report

## Executive Summary

Sample ID: `r params$sample_id`

This comprehensive report combines spectral analysis and metadata quality assessment to provide a complete evaluation of your NIR data.

## Spectral Analysis Results

### Quality Assessment
- **Quality Score**: `r params$spectral_quality_score` (`r params$spectral_quality_grade`)
- **Wavelength Range**: `r params$wavelength_range[1]` - `r params$wavelength_range[2]` nm
- **Data Points**: `r params$data_points`

### Detected Issues
`r ifelse(length(params$spectral_issues) > 0, paste("- ", params$spectral_issues, collapse = "\n- "), "No spectral issues detected")`

## Metadata Quality Results

### Overall Quality
- **Score**: `r params$metadata_quality_score` (`r params$metadata_quality_grade`)
- **Completeness**: `r params$metadata_completeness_score`%
- **Accuracy**: `r params$metadata_accuracy_score`%
- **Consistency**: `r params$metadata_consistency_score`%

### Standards Compliance
`r for (standard in names(params$metadata_standards)) {
  cat("- **", standard, "**: ", round(params$metadata_standards[[standard]], 1), "%\n")
}`

## Combined Recommendations

### Spectral Recommendations
`r ifelse(length(params$spectral_recommendations) > 0, paste("- ", params$spectral_recommendations, collapse = "\n- "), "No spectral recommendations")`

### Metadata Recommendations
`r ifelse(length(params$metadata_recommendations) > 0, paste("- ", params$metadata_recommendations, collapse = "\n- "), "No metadata recommendations")`

## Data Visualization

### Spectral Data
```{r}
if (exists("params$wavelengths") && exists("params$intensities")) {
  plot(params$wavelengths, params$intensities, type = "l", 
       xlab = "Wavelength (nm)", ylab = "Intensity", 
       main = "Spectral Data", col = "blue")
}
```

### Quality Metrics
```{r}
# Create quality metrics table
quality_data <- data.frame(
  Metric = c("Spectral Quality", "Metadata Quality", "Completeness", "Accuracy", "Consistency"),
  Score = c(params$spectral_quality_score, params$metadata_quality_score, 
            params$metadata_completeness_score, params$metadata_accuracy_score, params$metadata_consistency_score),
  Grade = c(params$spectral_quality_grade, params$metadata_quality_grade, 
            ifelse(params$metadata_completeness_score >= 75, "Good", "Needs Improvement"),
            ifelse(params$metadata_accuracy_score >= 75, "Good", "Needs Improvement"),
            ifelse(params$metadata_consistency_score >= 75, "Good", "Needs Improvement"))
)

print(xtable(quality_data), type = "html")
```
