---
title: "Comprehensive NIR Spectral Analysis Report"
author: "NIR Intelligence Platform"
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: true
    code-summary: "Show Python Code"
    fig-width: 10
    fig-height: 6
    css: styles.css
date: "`r Sys.Date()`"
params:
  sample_id: ""
  request_id: ""
  timestamp: ""
  overall_quality_score: 0
  processing_time: 0
  spectral_analysis: null
  metadata_quality: null
  calibration_results: null
  recommendations: []
  warnings: []
  errors: []
  include_source_code: true
  include_visualizations: true
  include_analysis_results: true
---

```{r setup, include=FALSE}
# Load required libraries
library(knitr)
library(ggplot2)
library(dplyr)
library(jsonlite)

# Set global options
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Custom function to check if parameter exists
param_exists <- function(param_name) {
  !is.null(params[[param_name]]) && !identical(params[[param_name]], "")
}
```

# Comprehensive NIR Spectral Analysis Report

## Executive Summary

This report presents the comprehensive analysis of NIR spectral data for sample **`r params$sample_id`** (Request ID: `r params$request_id`), conducted on `r params$timestamp`. The analysis includes spectral quality assessment, metadata validation, calibration evaluation, and actionable recommendations.

**Overall Quality Score: `r round(params$overall_quality_score, 2)` / 100**

**Processing Time: `r round(params$processing_time, 2)` seconds**

```{r summary-metrics, echo=FALSE}
# Display key metrics in a table
metrics <- data.frame(
  Metric = c("Overall Quality Score", "Processing Time (s)", "Recommendations", "Warnings", "Errors"),
  Value = c(
    round(params$overall_quality_score, 2),
    round(params$processing_time, 2),
    length(params$recommendations),
    length(params$warnings),
    length(params$errors)
  )
)

knitr::kable(metrics, caption = "Analysis Summary Metrics")
```

## Sample Information

- **Sample ID:** `r params$sample_id`
- **Request ID:** `r params$request_id`
- **Analysis Timestamp:** `r params$timestamp`
- **Processing Time:** `r round(params$processing_time, 2)` seconds

## Spectral Analysis Results

### Quality Assessment

```{r spectral-quality, echo=FALSE}
if (param_exists("spectral_analysis")) {
  spectral <- params$spectral_analysis
  
  quality_info <- data.frame(
    Aspect = c("Quality Grade", "Quality Score", "Data Points", "Wavelength Range"),
    Value = c(
      spectral$quality_grade,
      round(spectral$quality_score, 2),
      spectral$data_points,
      paste0("[", spectral$wavelength_range[1], ", ", spectral$wavelength_range[2], "] nm")
    )
  )
  
  knitr::kable(quality_info, caption = "Spectral Quality Metrics")
}
```

### Signal Quality Metrics

```{r signal-metrics, echo=FALSE}
if (param_exists("spectral_analysis")) {
  spectral <- params$spectral_analysis
  
  signal_metrics <- data.frame(
    Metric = c("Noise Level", "Signal-to-Noise Ratio", "Baseline Quality", "Peak Detection"),
    Value = c(
      round(spectral$noise_level, 4),
      round(spectral$signal_to_noise_ratio, 2),
      spectral$baseline_quality,
      ifelse(is.null(spectral$peaks_detected), "N/A", length(spectral$peaks_detected))
    )
  )
  
  knitr::kable(signal_metrics, caption = "Signal Quality Metrics")
}
```

### Detected Issues

```{r spectral-issues, echo=FALSE}
if (param_exists("spectral_analysis") && length(params$spectral_analysis$issues_detected) > 0) {
  cat("**Detected Spectral Issues:**\n\n")
  for (issue in params$spectral_analysis$issues_detected) {
    cat("- ", issue, "\n")
  }
} else {
  cat("No spectral issues detected.\n")
}
```

### Parameter Recommendations

```{r parameter-recommendations, echo=FALSE}
if (param_exists("spectral_analysis") && param_exists("spectral_analysis$parameter_recommendations")) {
  recommendations <- params$spectral_analysis$parameter_recommendations
  
  if (length(recommendations) > 0) {
    cat("**Parameter Recommendations:**\n\n")
    for (rec in recommendations) {
      if (is.list(rec)) {
        cat(sprintf("- **%s:** Current: %s, Recommended: %s\n  - Reason: %s\n  - Impact: %s\n",
                    rec$parameter_name, rec$current_value, rec$recommended_value, rec$reasoning, rec$impact))
      } else if (is.character(rec)) {
        cat("- ", rec, "\n")
      }
    }
  } else {
    cat("No parameter recommendations.\n")
  }
} else {
  cat("No parameter recommendations available.\n")
}
```

## Metadata Quality Assessment

### Overall Metadata Quality

```{r metadata-quality, echo=FALSE}
if (param_exists("metadata_quality")) {
  metadata <- params$metadata_quality
  
  quality_info <- data.frame(
    Aspect = c("Completeness Score", "Standards Compliance", "Overall Quality Grade"),
    Value = c(
      round(metadata$completeness_score, 2),
      round(metadata$standards_compliance, 2),
      metadata$quality_grade
    )
  )
  
  knitr::kable(quality_info, caption = "Metadata Quality Metrics")
}
```

### Standards Compliance

```{r standards-compliance, echo=FALSE}
if (param_exists("metadata_quality") && param_exists("metadata_quality$standards_checked")) {
  standards <- params$metadata_quality$standards_checked
  
  if (length(standards) > 0) {
    cat("**Standards Checked:**\n\n")
    for (standard in standards) {
      cat("- ", standard, "\n")
    }
  }
}
```

### Missing Fields and Enhancements

```{r missing-fields, echo=FALSE}
if (param_exists("metadata_quality")) {
  metadata <- params$metadata_quality
  
  if (length(metadata$missing_required_fields) > 0) {
    cat("**Missing Required Fields:**\n\n")
    for (field in metadata$missing_required_fields) {
      cat("- ", field, "\n")
    }
    cat("\n")
  }
  
  if (length(metadata$missing_optional_fields) > 0) {
    cat("**Missing Optional Fields:**\n\n")
    for (field in metadata$missing_optional_fields) {
      cat("- ", field, "\n")
    }
    cat("\n")
  }
  
  if (length(metadata$enhancement_suggestions) > 0) {
    cat("**Enhancement Suggestions:**\n\n")
    for (suggestion in metadata$enhancement_suggestions) {
      cat("- ", suggestion, "\n")
    }
  }
}
```

## Visualizations

### Spectral Data Plot

```{r spectral-plot, echo=FALSE, fig.cap="Spectral Data Visualization", fig.alt="Spectral data plot showing intensity vs wavelength"}
if (param_exists("spectral_analysis") && 
    param_exists("spectral_analysis$wavelengths") && 
    param_exists("spectral_analysis$intensities")) {
  
  spectral <- params$spectral_analysis
  
  # Create data frame
  spectral_df <- data.frame(
    Wavelength = spectral$wavelengths,
    Intensity = spectral$intensities
  )
  
  # Plot spectral data
  ggplot(spectral_df, aes(x = Wavelength, y = Intensity)) +
    geom_line(color = "#1f77b4", linewidth = 0.8) +
    geom_point(color = "#ff7f0e", size = 1) +
    labs(title = "NIR Spectral Data", 
         subtitle = paste("Sample:", params$sample_id), 
         x = "Wavelength (nm)", 
         y = "Intensity") +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5, face = "bold"))
}
```

### Quality Metrics Visualization

```{r quality-metrics-plot, echo=FALSE, fig.cap="Quality Metrics Comparison", fig.alt="Bar chart showing various quality metrics"}
if (param_exists("spectral_analysis") && param_exists("metadata_quality")) {
  spectral <- params$spectral_analysis
  metadata <- params$metadata_quality
  
  # Prepare metrics
  metrics <- data.frame(
    Category = c("Spectral Quality", "Metadata Completeness", "Standards Compliance", "Overall Quality"),
    Score = c(
      spectral$quality_score,
      metadata$completeness_score * 100,
      metadata$standards_compliance * 100,
      params$overall_quality_score
    )
  )
  
  # Plot
  ggplot(metrics, aes(x = Category, y = Score, fill = Category)) +
    geom_bar(stat = "identity", width = 0.6) +
    geom_text(aes(label = round(Score, 1)), vjust = -0.5, size = 3.5) +
    labs(title = "Quality Metrics Comparison", 
         x = "Metric", 
         y = "Score") +
    scale_y_continuous(limits = c(0, 100)) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}
```

## Analysis Source Code

The following Python code was used to perform the spectral analysis:

```{python analysis-code, echo=TRUE, eval=FALSE}
# NIR Spectral Analysis Code
# Generated by NIR Intelligence Platform

import numpy as np
import pandas as pd
from scipy import signal as scipy_signal
from typing import Dict, List, Any, Optional
from dataclasses import dataclass
from enum import Enum

class QualityGrade(Enum):
    EXCELLENT = "A"
    GOOD = "B"
    FAIR = "C"
    POOR = "D"
    UNACCEPTABLE = "F"

@dataclass
class SpectralAnalysisResult:
    quality_score: float
    quality_grade: QualityGrade
    wavelengths: List[float]
    intensities: List[float]
    data_points: int
    wavelength_range: List[float]
    noise_level: float
    signal_to_noise_ratio: float
    baseline_quality: str
    peaks_detected: List[float]
    issues_detected: List[str]
    parameter_recommendations: List[Dict[str, Any]]
    preprocessing_steps: List[str]
    quality_metrics: Dict[str, float]

class SpectralAnalyzer:
    def __init__(self):
        self.quality_thresholds = {
            "excellent": 90,
            "good": 80,
            "fair": 70,
            "poor": 60
        }
    
    def calculate_quality_score(self, wavelengths: List[float], intensities: List[float]) -> float:
        """Calculate overall quality score from spectral data"""
        # Calculate various quality metrics
        noise_level = self._calculate_noise_level(intensities)
        snr = self._calculate_signal_to_noise(intensities)
        baseline_quality = self._assess_baseline(intensities)
        
        # Weighted score calculation
        score = 0.0
        weights = {"noise": 0.3, "snr": 0.3, "baseline": 0.2, "data_points": 0.2}
        
        # Normalize and weight each metric
        score += (1 - noise_level) * weights["noise"] * 100
        score += min(snr / 100, 1.0) * weights["snr"] * 100
        score += self._quality_to_score(baseline_quality) * weights["baseline"] * 100
        score += min(len(wavelengths) / 1000, 1.0) * weights["data_points"] * 100
        
        return min(max(score, 0), 100)
    
    def _calculate_noise_level(self, intensities: List[float]) -> float:
        """Calculate noise level from intensity data"""
        if len(intensities) < 10:
            return 1.0  # High noise for insufficient data
        
        # Calculate standard deviation as noise estimate
        noise_std = np.std(intensities)
        signal_mean = np.mean(intensities)
        
        if signal_mean == 0:
            return 1.0
        
        return min(noise_std / signal_mean, 1.0)
    
    def _calculate_signal_to_noise(self, intensities: List[float]) -> float:
        """Calculate signal-to-noise ratio"""
        if len(intensities) < 10:
            return 0.0
        
        signal_mean = np.mean(intensities)
        noise_std = np.std(intensities)
        
        if noise_std == 0:
            return 100.0
        
        return signal_mean / noise_std
    
    def _assess_baseline(self, intensities: List[float]) -> str:
        """Assess baseline quality"""
        # Simple baseline assessment based on first and last 10% of data
        n = len(intensities)
        if n < 20:
            return "Poor"
        
        first_part = np.mean(intensities[:n//10])
        last_part = np.mean(intensities[-n//10:])
        middle_part = np.mean(intensities[n//10:9*n//10])
        
        # Check if baseline is relatively flat
        baseline_variation = abs(first_part - last_part) / max(abs(middle_part), 1)
        
        if baseline_variation < 0.1:
            return "Excellent"
        elif baseline_variation < 0.2:
            return "Good"
        elif baseline_variation < 0.3:
            return "Fair"
        else:
            return "Poor"
    
    def _quality_to_score(self, quality: str) -> float:
        """Convert quality string to numerical score"""
        quality_map = {"Excellent": 1.0, "Good": 0.8, "Fair": 0.6, "Poor": 0.4, "Unacceptable": 0.2}
        return quality_map.get(quality, 0.5)

# Example usage
if __name__ == "__main__":
    analyzer = SpectralAnalyzer()
    
    # This would be replaced with actual spectral data
    wavelengths = [400, 450, 500, 550, 600, 650, 700, 750, 800, 850, 900, 950, 1000]
    intensities = [0.1, 0.15, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.75, 0.6, 0.4, 0.2]
    
    quality_score = analyzer.calculate_quality_score(wavelengths, intensities)
    print(f"Quality Score: {quality_score:.2f}")
```

## Data Preprocessing Code

```{python preprocessing-code, echo=TRUE, eval=FALSE}
# Data Preprocessing Code
# Used for cleaning and preparing spectral data

import numpy as np
import pandas as pd
from scipy import signal as scipy_signal
from typing import Dict, List, Any, Optional, Tuple

class DataPreprocessor:
    """Comprehensive data preprocessing for NIR spectral analysis"""
    
    def __init__(self):
        self.preprocessing_methods = [
            "SNV", "MSC", "Savitzky-Golay", "BaselineCorrection", "Detrending"
        ]
    
    def apply_snv(self, intensities: List[float]) -> List[float]:
        """Apply Standard Normal Variate (SNV) correction"""
        intensities_array = np.array(intensities)
        mean_val = np.mean(intensities_array)
        std_val = np.std(intensities_array)
        
        if std_val == 0:
            return intensities
        
        return ((intensities_array - mean_val) / std_val).tolist()
    
    def apply_msc(self, intensities: List[float], reference: Optional[List[float]] = None) -> List[float]:
        """Apply Multiplicative Scatter Correction (MSC)"""
        if reference is None:
            reference = intensities
        
        intensities_array = np.array(intensities)
        reference_array = np.array(reference)
        
        # Simple MSC implementation
        mean_ref = np.mean(reference_array)
        mean_int = np.mean(intensities_array)
        
        if mean_ref == 0 or mean_int == 0:
            return intensities
        
        # Scale and offset correction
        scaled = intensities_array * (mean_ref / mean_int)
        return scaled.tolist()
    
    def apply_savitzky_golay(self, intensities: List[float], window_size: int = 5, polyorder: int = 2) -> List[float]:
        """Apply Savitzky-Golay smoothing"""
        try:
            intensities_array = np.array(intensities)
            smoothed = scipy_signal.savgol_filter(intensities_array, window_size, polyorder)
            return smoothed.tolist()
        except Exception:
            return intensities
    
    def apply_baseline_correction(self, intensities: List[float]) -> List[float]:
        """Apply baseline correction using polynomial fitting"""
        intensities_array = np.array(intensities)
        x = np.arange(len(intensities_array))
        
        # Fit a polynomial to the baseline
        try:
            coefficients = np.polyfit(x, intensities_array, 2)
            baseline = np.polyval(coefficients, x)
            corrected = intensities_array - baseline
            return corrected.tolist()
        except Exception:
            return intensities
    
    def preprocess_data(self, wavelengths: List[float], intensities: List[float], 
                       methods: List[str] = None) -> Tuple[List[float], List[str]]:
        """Apply multiple preprocessing methods"""
        if methods is None:
            methods = self.preprocessing_methods
        
        processed_intensities = intensities.copy()
        applied_methods = []
        
        for method in methods:
            try:
                if method == "SNV":
                    processed_intensities = self.apply_snv(processed_intensities)
                    applied_methods.append("SNV")
                elif method == "MSC":
                    processed_intensities = self.apply_msc(processed_intensities)
                    applied_methods.append("MSC")
                elif method == "Savitzky-Golay":
                    processed_intensities = self.apply_savitzky_golay(processed_intensities)
                    applied_methods.append("Savitzky-Golay")
                elif method == "BaselineCorrection":
                    processed_intensities = self.apply_baseline_correction(processed_intensities)
                    applied_methods.append("BaselineCorrection")
                elif method == "Detrending":
                    processed_intensities = self._apply_detrending(processed_intensities)
                    applied_methods.append("Detrending")
            except Exception:
                continue
        
        return processed_intensities, applied_methods
    
    def _apply_detrending(self, intensities: List[float]) -> List[float]:
        """Apply detrending to remove linear trends"""
        intensities_array = np.array(intensities)
        x = np.arange(len(intensities_array))
        
        # Fit a line and remove it
        coefficients = np.polyfit(x, intensities_array, 1)
        trend = np.polyval(coefficients, x)
        detrended = intensities_array - trend
        return detrended.tolist()

# Example preprocessing
if __name__ == "__main__":
    preprocessor = DataPreprocessor()
    
    # Sample data
    wavelengths = [400, 450, 500, 550, 600, 650, 700, 750, 800, 850, 900, 950, 1000]
    intensities = [0.1, 0.15, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.75, 0.6, 0.4, 0.2]
    
    # Apply preprocessing
    processed, methods = preprocessor.preprocess_data(wavelengths, intensities)
    print(f"Applied preprocessing methods: {methods}")
```

## Recommendations and Next Steps

### Summary of Recommendations

```{r recommendations-summary, echo=FALSE}
if (length(params$recommendations) > 0) {
  cat("Based on the analysis, the following recommendations are provided:\n\n")
  for (i in seq_along(params$recommendations)) {
    cat(sprintf("%d. %s\n", i, params$recommendations[i]))
  }
} else {
  cat("No specific recommendations. The spectral data appears to be of good quality.\n")
}
```

### Warnings and Issues

```{r warnings-summary, echo=FALSE}
if (length(params$warnings) > 0) {
  cat("**Warnings:**\n\n")
  for (warning in params$warnings) {
    cat("- ", warning, "\n")
  }
  cat("\n")
}

if (length(params$errors) > 0) {
  cat("**Errors:**\n\n")
  for (error in params$errors) {
    cat("- ", error, "\n")
  }
}
```

## Technical Details

### Analysis Configuration

- **Analysis Mode:** Comprehensive
- **Privacy Level:** Local Only
- **Report Format:** HTML
- **Include Calibration:** Yes
- **Include Federated Learning:** No

### System Information

- **NIR Intelligence Platform Version:** 1.0.0
- **Report Generated:** `r Sys.time()`
- **Analysis Engine:** CrewAI with specialized NIR agents
- **Visualization Tools:** ggplot2, knitr

### Data Standards Compliance

This report follows open science principles and adheres to established NIR spectroscopy standards including:
- ASTM E1655 (Standard Practices for Infrared Multivariate Quantitative Analysis)
- ISO 12099 (Near Infrared Spectrometry)
- EURACHEM guidelines for analytical chemistry

---

*This report was automatically generated by the NIR Intelligence Platform. For questions or support, please refer to the platform documentation.*