---
title: "NIR Spectral Comparison Report"
author: "NIR Intelligence Platform"
format: html
date: "`r Sys.Date()`"
---

# NIR Spectral Comparison Report

## Comparison Overview

Number of samples: `r length(params$samples)`

## Sample Information

```{r}
sample_info <- data.frame(
  Sample = names(params$samples),
  Quality = sapply(params$samples, function(s) s$quality_grade),
  Score = sapply(params$samples, function(s) s$quality_score),
  Wavelength.Range = sapply(params$samples, function(s) paste(s$wavelength_range, collapse = "-")),
  Data.Points = sapply(params$samples, function(s) s$data_points)
)

print(xtable(sample_info), type = "html")
```

## Comparative Analysis

### Quality Comparison
```{r}
quality_scores <- sapply(params$samples, function(s) s$quality_score)
names(quality_scores) <- names(params$samples)

barplot(quality_scores, main = "Spectral Quality Score Comparison", 
        ylab = "Quality Score", xlab = "Sample", col = "skyblue")
```

## Detailed Sample Reports

`r for (sample_name in names(params$samples)) {
  sample <- params$samples[[sample_name]]
  cat("### ", sample_name, "\n\n")
  cat("- **Quality Score**: ", sample$quality_score, " (", sample$quality_grade, ")\n")
  cat("- **Wavelength Range**: ", sample$wavelength_range[1], "-", sample$wavelength_range[2], " nm\n")
  cat("- **Issues**: ", paste(sample$issues_detected, collapse = ", "), "\n\n")
}`
